### 2020-05-30 writeup/transfer.tex

On the positive side, we describe two implications for positive transfer, assuming that $\norm{\beta_1 - \beta_2}^2$ is small in the isotropic model.

@@

\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
	In the isotropic model, assume that $\rho_1,\rho_2 > 1$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
	Let $$ the data efficiency ratio is bounded within
	$[ ]$
\end{proposition}
The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.

>>>>

On the positive side, we describe two implications for positive transfer, assuming that $\Psi(\beta_1, \beta_2)$ is small in the isotropic model.

@@

\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
	In the isotropic model, assume that $\rho_1,\rho_2 > 1$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
	Then the data efficiency ratio is at least \[ \frac{1}{\rho_1 + \rho_2}\cdot \bigbrace{1 + \frac{1}{\rho_1^{-1} + \rho_2^{-1} - 2\Psi(\beta_1, \beta_2)}}. \]
\end{proposition}
The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.
